### 2018-05-16 msc_diploma_cubesat_galgoczi.tex
images

@@

Gamma-ray bursts (GRBs) [1, 2, 3, 4, 5, 6, 7, 8, 9] have been studied already about four decades, nonetheless their origin is still not fully understood. They are one of the most extreme explosive events ever observed. In spite of tremendous effort and numerous observations there are still open questions concerning their detailed physics. GRBs were discovered in years 1967–73 by military Vela satellites and later reported to the scientific community in early seventies [10, 11]. They occur roughly once per day and are characterized by flashes of $\gamma$-rays typically lasting from a fraction of a second to thousands of seconds, typically in the energy range from several keV to several MeV, however $\gamma$-rays of energy >1 GeV associated with GRBs were detected as well. A GRB event outshines any other gamma-ray source on the sky.
It has been found that the duration distribution of their $\gamma$-ray prompt emission is bimodial [12] which suggested that there were two groups of GRBs. Later, based on more observations, it has been confirmed that these two GRB groups were two distinct astrophysical populations [12, 13, 14, 15, 16,17]: I. so called long GRBs (LGRBs) with softer spectrum and with prompt $\gamma$-ray emission $\geqslant$2 s that were identified to be gravitational collapses of massive stars due to their association with type Ic core-collapse supernovae, and II. so called short GRBs (SGRBs) with harder spectrum and with prompt $\gamma$-ray emission $\leqslant$2 s originating in merger of two compact objects such as neutron star - neutron star (NS-NS) or neutron star - black hole (NS-BH) [18].

@@

It was proposed that GRBs were created in collisions of highly relativistic outflow of the accelerated jetted matter [19, 20]. In many cases it was found that the prompt $\gamma$-ray emission is followed by longer-lasting afterglow in soft X-ray, optical or radio waves [21, 22] explained as a result of the propagation of a relativistic shockwave through the circumburst medium. The suggestion that GRBs lie at cosmological distances [23] was confirmed by numerous observations and it was found that their redshifts are up to z=9.4 with $\langle$ z $\rangle\approx$0.5 for SGRBs and $\langle$z$\rangle \approx$2.0 for LGRBs [18]. The energy content 51 released in a GRB is $\sim$10 erg.
In some cases of LGRBs there was observed supernova component in the lightcurve or in the spectrum of its afterglow, peaking $\sim$2 weeks after the initial trigger [24, 25, 26]. LGRBs are associated with the brightest regions of galaxies and with the most massive stars [27]. The relativistic outflow of LGRBs has a bulk Lorentz factor of $\Gamma\sim$300 [5]. The afterglow observations indicate that a geometrical beaming of the LGRBs radiation has an opening angle of $\sim$5 [28].

@@

Observations suggest that SGRBs arise from old astrophysical populations. The beaming angles for SGRBs jets seems to be from $\sim$5 to > 25 [5, 29, 30]. The model that they originate in the merger of two NS has been recently confirmed by the detection of the gravitational wave (GW) signal by LIGO / Virgo collaboration 1, 2. This GW signal was accompanied with a SGRB detected by the Fermi /Gamma-ray Burst Monitor (GBM) and INTEGRAL instruments followed by the observation of the GRB’s afterglow and its host galaxy [31, 32, 33]. In case of SGRBs a kilonova/macronova can be observed. It emits electromagnetic radiation due to the radioactive decay of heavy r-process nuclei that are produced and ejected almost isotropically during the merger process [34].

@@

In spite of great theoretical and observational successes over the last four decades, many key questions remain about the physics of GRBs. For a detailed review see [3, 4, 6, 35]. Some of these key questions are following.

@@

First stars (Pop III): what is the expected signature of GRBs originating in the death of the first metal-free massive stars at high redshift? It was estimated that the mass of the BH at the center of the collapsar of Pop III star is a factor of ten larger and Pop III GRBs may thus tend to have larger durations than those of ordinary Pop I and Pop II GRBs [36].

@@

Recent detection of the electromagnetic (EM) signal of the short GRB 170817A [37] associated with a GW signal GW170817 produced by a binary neutron star (BNS) merger [32] marks a milestone in the multi-messenger research of GRBs and means a great importance of the efforts of searching for EM counterparts to GW sources with spaceborn instruments. The discovery was made on August 17, 2017 at 12:41:06 UTC with the Fermi/GBM which detected and triggered on the short gamma-ray burst GRB 170817A. Approximately 1.7 prior to this GRB, LIGO-Virgo detector network observed a GW signal GW170817 at 12:41:04.4 UTC which originated from a BNS inspiral. The source was localized 9/89within a sky region of 28 deg 2 (90 \% probability), which was the most precisely localized GW signal yet. An extensive observing campaign was launched across the electromagnetic spectrum [33] leading to the discovery of a bright optical transient in NGC 4993. Observations in $\gamma$-ray, X-ray, and ultraviolet (UV) wavelengths include also INTEGRAL [38], Chandra X-ray Observatory [39], Swift and Nuclear Spectroscopic Telescope ARray (NuSTAR) were performed and a blue kilonova associated with this event was detected [40].
Some models predict also EM signal from BBH coalescence, for example [41, 42]. More detections of EM counterpart to GW sources and kilonovae are indeed essential for better understanding of these phenomena and this proposed mission has a great potential to bring new and valuable observational data.
After the upgrades of LIGO, following the finished observing run O2, there will be O3 run scheduled to start in 2018. Further observing runs are expected after next improve of the sensitivity. Designed sensitivity is aimed to be achieved in 2021. The Kamioka Gravitational Wave Detector (KAGRA) 3 is expected to start the first cryogenic operation in 2018, and the observing runs with a full interferometer are expected in 2020s [43]. Therefore, more GW detections are expected during the operation of this proposed mission.

@@

Various detector types has been used or are planned for space instruments for example gas-filled detectors like proportional counters and Geiger counters; scintillation detectors like inorganic crystal scintillators, e.g. NaI(Tl) or CsI(Tl), and plastic scintillators; semiconductor devices like, e.g. cryogenically cooled germanium, Cadmium Zinc Telluride (CZT) or Silicon Drift Detector (SDD) technique. Other types of detectors used in space missions are Compton scatter telescopes or pair production telescopes. Table 3 lists detector technologies capable of detecting GRBs in hard X-ray and gamma-ray range employed in previous and current major instruments. For an extensive review of hard X-ray / soft gamma-ray experiments and missions see [47].

@@

Fermi 7 [44, 45, 66] was launched in 2008 and the main instruments are the Large Area Telescope (LAT) and the Gamma-ray Burst Monitor. 
Neil Gehrels Swift Observatory (Swift) 8 [64, 67] was launched in 2005 and the main instruments are
Burst Alert Telescope (BAT), X-ray Telescope (XRT), and UV/Optical Telescope (UVOT).
INTErnational Gamma-Ray Astrophysics Laboratory (INTEGRAL) 9 [57, 58, 68, 69] was launched in
2002 Among several instruments on board INTEGRAL the ones which detect most of GRBs are the Anti-Coincidence Shield of the SPectrometer of INTEGRAL (SPI-ACS) and the Integral Soft Gamma-Ray Imager (ISGRI) detector layer of the Imager on Board the Integral Satellite (IBIS).
Wind/Konus 10 [70] was launched in 1994 and its still active GRB instrument is Konus.
Astro-Rivelatore Gamma a Immagini Leggero (AGILE) 11 /Super-AGILE [48, 71] was launched in
2007 and its Hard X-ray Imaging Detector (Super-AGILE) detected several GRBs.
CALorimetric Electron Telescope (CALET) 12 [52, 72, 73] / Gamma-Ray Burst Monitor (CGBM), was launched in 2015 and it is placed on the International Space Station (ISS).

Monitor of All-sky X-ray Image (MAXI) 13 [60, 74 ], started nominal observation in 2009. Its instrument Gas Slit Camera (GSC) detects GRBs. The instrument is placed on ISS.
Gamma-ray Burst Polarimeter POLAR 14 [61, 75], was launched in 2016 and is dedicated to the measurement of GRB polarization.
Lomonosov 15 /BDRG [59, 76], was launched in 2016. The BDRG instrument on board detected several GRBs.
The Hard X-ray Modulation Telescope (Insight-HXMT) 16 [56, 77], was launched in 2017. It has on board the high energy X-ray telescope (HE), the medium energy X-ray telescope, and the low energy X-ray telescope.
ASTROSAT 17 [49, 78, 79], was launched in 2015 and its Cadmium Zinc Telluride Imager (CZTI) has already detected many GRBs.
Reuven Ramaty High Energy Solar Spectroscopic Imager (RHESSI) 18 [62, 80, 81], was launched in 2002. It is designed to study hard x-ray and gamma-ray emission from solar flares, however it is also efficient instrument to detect non-solar gamma-ray events like GRBs.
The energy range, FoV and localization accuracy for the instruments of the current missions which observe GRBs is summarized in Table 4. Figure 3 shows the FoV vs. localization accuracy of the current instruments which detect GRBs. For comparison the specification of this project is shown as
well.

@@

Our project can potentially contribute to some of the currently operating GRB collection and alertnetworks such as the following ones:
The InterPlanetary Network (IPN) 27 [97, 98] which derives the positions of fast gamma-ray transients of all kinds by triangulation. Numerous spacecraft and instruments participate in the network at the Earth’s orbit as well as in the interplanetary space. It detects about 350/year.
The Gamma-ray Coordinates Network (Transient Astronomy Network) (GCN/TAN) 28 provides information about GRBs in real-time to the world community. The network provides the real-time (and near real-time) distribution of GRB locations, images, spectra, and lightcurves detected by various spacecraft and the distribution of follow-up observation reports.
The Global Relay of Observatories Watching Transients Happen (GROWTH) 29 is an international scientific collaborative project studying the astronomical transients.

@@

This cubesat project will provide high precision localization accuracy of GRBs allowing efficient follow-up observations by existing ground based observatories. There are several observatories world-wide to perform photometric or spectroscopic observations of GRB afterglows, for example:
The Mobile Astronomical System of TElescope Robots (MASTER) 30 [99] is a global network of robotic telescopes for very fast positioning and follow up of GRBs.
The Burst Optical Observer and Transient Exploring System (BOOTES) network of robotic telescopes for follow up observations of GRBs. 31 [100] is a world wide The Robotic Optical Transient Search Experiment (ROTSE) 32 [101] are telescopes which operate at
sites around the world and follow GRBs.
Pi of the Sky 33 [102] is a system of detectors designed for continuous observation of night sky looking for optical flashes of astrophysical origin, in particular for GRBs.
Several other telescopes and observatories which provide measurements in optical, infra-red or radio bands are also, e.g.: Gamma-Ray Burst Optical/Near-Infrared Detector (GROND) 34 , the Palomar 60 inch telescope 35 , Rapid Eye Mount (REM) 36 , Livermore Optical Transient Imaging System (Super- LOTIS) 37 , Télescopes à Action Rapide pour les Objets Transitoires (TAROT) 38 , Gran Telescopio Canarias (GTC) 39 , ESO Very Large Telescope (VLT) 40 , Nordic Optical Telescope (NOT) 41 , Observatorio Astronómico Nacional on the Sierra de San Pedro Mártir 42 , Cerro Tololo Inter-American Observatory (CTIO) 43 , Telescopio Nazionale Galileo (TNG) 44 , Gao-Mei-Gu (GMG) station of Yunnan Observatories 45 , Observatorio de Sierra Nevada (OSN) 46 , United Kingdom Infrared Telescope (UKIRT) 47 , Very Large Array (VLA) 48 , Atacama Large Millimeter/Submillimeter Array (ALMA) 49 , James Clerk Maxwell Telescope 50 , Arcminute Microkelvin Imager which robotically triggers on Swift GRBs (AMI-GRB) 51 .

\subsection{Aim of the simulation}

\subsection{The Constellation Gamma (ConGa) fleet}

The main aim of the paper, therefore this thesis is to optimize the scintillators of the CubeSats (miniaturized satellites) in the Constellation Gamma satellites. The second aim is to understand how the material of the CubeSat would affect the gamma photons that the satellite is meant to detect.

@@

@@

@@

@@

@@

@@

\bibitem{tgemadv} C. Shalem, R. Chechik, et al.,\\
Advances in Thick GEM-like gaseous electron multipliers—Part I: atmospheric pressure operation,\\
Nuclear Instruments and Methods in Physics Research A, vol. 558, page 475-489, 2006

>>>>

The main aim of the paper, therefore this thesis is to optimize the scintillators of the CubeSats (miniaturized satellites) in the Constellation Gamma satellites. It is not known which would be the best detector configuration for the detection of GRBs. In the

 The second aim is to understand how the material of the CubeSat would affect the gamma photons that the satellite is meant to detect.

@@

Gamma-ray bursts (GRBs) \cite{grb1,grb2,grb3,grb4} have been studied already about four decades, nonetheless their origin is still not fully understood. They are one of the most extreme explosive events ever observed. In spite of tremendous effort and numerous observations there are still open questions concerning their detailed physics. GRBs were discovered in years 1967–73 by military Vela satellites and later reported to the scientific community in early seventies \cite{grb5}. They occur roughly once per day and are characterized by flashes of $\gamma$-rays typically lasting from a fraction of a second to thousands of seconds, typically in the energy range from several keV to several MeV, however $\gamma$-rays of energy >1 GeV associated with GRBs were detected as well. A GRB event outshines any other gamma-ray source on the sky.
It has been found that the duration distribution of their $\gamma$-ray prompt emission is bimodial \cite{grb6} which suggested that there were two groups of GRBs. Later, based on more observations, it has been confirmed that these two GRB groups were two distinct astrophysical populations \cite{grb6,grb7,grb8}: I. so called long GRBs (LGRBs) with softer spectrum and with prompt $\gamma$-ray emission $\geqslant$2 s that were identified to be gravitational collapses of massive stars due to their association with type Ic core-collapse supernovae, and II. so called short GRBs (SGRBs) with harder spectrum and with prompt $\gamma$-ray emission $\leqslant$2 s originating in merger of two compact objects such as neutron star - neutron star (NS-NS) or neutron star - black hole (NS-BH) \cite{grb9}.

@@

It was proposed that GRBs were created in collisions of highly relativistic outflow of the accelerated jetted matter \cite{grb10}. In many cases it was found that the prompt $\gamma$-ray emission is followed by longer-lasting afterglow in soft X-ray, optical or radio waves \cite{grb11} explained as a result of the propagation of a relativistic shockwave through the circumburst medium. The suggestion that GRBs lie at cosmological distances \cite{grb12} was confirmed by numerous observations and it was found that their redshifts are up to z=9.4 with $\langle$ z $\rangle\approx$0.5 for SGRBs and $\langle$z$\rangle \approx$2.0 for LGRBs [18]. The energy content 51 released in a GRB is $\sim$10 erg.
In some cases of LGRBs there was observed supernova component in the lightcurve or in the spectrum of its afterglow, peaking $\sim$2 weeks after the initial trigger \cite{grb13}. LGRBs are associated with the brightest regions of galaxies and with the most massive stars \cite{grb14}. The relativistic outflow of LGRBs has a bulk Lorentz factor of $\Gamma\sim$300 [5]. The afterglow observations indicate that a geometrical beaming of the LGRBs radiation has an opening angle of $\sim$5 \cite{grb15}.

@@

Observations suggest that SGRBs arise from old astrophysical populations. The beaming angles for SGRBs jets seems to be from $\sim$5 to > 25 \cite{grb16}. The model that they originate in the merger of two NS has been recently confirmed by the detection of the gravitational wave (GW) signal by LIGO / Virgo collaboration 1, 2. This GW signal was accompanied with a SGRB detected by the Fermi /Gamma-ray Burst Monitor (GBM) and INTEGRAL instruments followed by the observation of the GRB’s afterglow and its host galaxy \cite{grb17}. In case of SGRBs a kilonova/macronova can be observed. It emits electromagnetic radiation due to the radioactive decay of heavy r-process nuclei that are produced and ejected almost isotropically during the merger process \cite{grb18}.

@@

In spite of great theoretical and observational successes over the last four decades, many key questions remain about the physics of GRBs. For a detailed review see \cite{grb19}. Some of these key questions are following.

@@

First stars (Pop III): what is the expected signature of GRBs originating in the death of the first metal-free massive stars at high redshift? It was estimated that the mass of the BH at the center of the collapsar of Pop III star is a factor of ten larger and Pop III GRBs may thus tend to have larger durations than those of ordinary Pop I and Pop II GRBs \cite{grb20}.

@@

Recent detection of the electromagnetic (EM) signal of the short GRB 170817A \cite{grb21} associated with a GW signal GW170817 produced by a binary neutron star (BNS) merger \cite{grb17} marks a milestone in the multi-messenger research of GRBs and means a great importance of the efforts of searching for EM counterparts to GW sources with spaceborn instruments. The discovery was made on August 17, 2017 at 12:41:06 UTC with the Fermi/GBM which detected and triggered on the short gamma-ray burst GRB 170817A. Approximately 1.7 prior to this GRB, LIGO-Virgo detector network observed a GW signal GW170817 at 12:41:04.4 UTC which originated from a BNS inspiral. The source was localized 9/89within a sky region of 28 deg 2 (90 \% probability), which was the most precisely localized GW signal yet. An extensive observing campaign was launched across the electromagnetic spectrum leading to the discovery of a bright optical transient in NGC 4993. Observations in $\gamma$-ray, X-ray, and ultraviolet (UV) wavelengths include also INTEGRAL \cite{grb22}, Chandra X-ray Observatory \cite{grb23}, Swift and Nuclear Spectroscopic Telescope ARray (NuSTAR) were performed and a blue kilonova associated with this event was detected \cite{grb24}.
Some models predict also EM signal from BBH coalescence, for example \cite{grb25}. More detections of EM counterpart to GW sources and kilonovae are indeed essential for better understanding of these phenomena and this proposed mission has a great potential to bring new and valuable observational data.
After the upgrades of LIGO, following the finished observing run O2, there will be O3 run scheduled to start in 2018. Further observing runs are expected after next improve of the sensitivity. Designed sensitivity is aimed to be achieved in 2021. The Kamioka Gravitational Wave Detector (KAGRA) 3 is expected to start the first cryogenic operation in 2018, and the observing runs with a full interferometer are expected in 2020s \cite{grb26}. Therefore, more GW detections are expected during the operation of this proposed mission.

@@

Various detector types has been used or are planned for space instruments for example gas-filled detectors like proportional counters and Geiger counters; scintillation detectors like inorganic crystal scintillators, e.g. NaI(Tl) or CsI(Tl), and plastic scintillators; semiconductor devices like, e.g. cryogenically cooled germanium, Cadmium Zinc Telluride (CZT) or Silicon Drift Detector (SDD) technique. Other types of detectors used in space missions are Compton scatter telescopes or pair production telescopes. Table 3 lists detector technologies capable of detecting GRBs in hard X-ray and gamma-ray range employed in previous and current major instruments. For an extensive review of hard X-ray / soft gamma-ray experiments and missions see \cite{grb30}.

@@

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/fovvsloc.png}
\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
\end{figure}

Fermi 7 \cite{grb28} was launched in 2008 and the main instruments are the Large Area Telescope (LAT) and the Gamma-ray Burst Monitor. 
Neil Gehrels Swift Observatory (Swift) 8 \cite{grb31} was launched in 2005 and the main instruments are
Burst Alert Telescope (BAT), X-ray Telescope (XRT), and UV/Optical Telescope (UVOT).
INTErnational Gamma-Ray Astrophysics Laboratory (INTEGRAL) 9 \cite{grb32} was launched in
2002 Among several instruments on board INTEGRAL the ones which detect most of GRBs are the Anti-Coincidence Shield of the SPectrometer of INTEGRAL (SPI-ACS) and the Integral Soft Gamma-Ray Imager (ISGRI) detector layer of the Imager on Board the Integral Satellite (IBIS).
Wind/Konus 10 \cite{grb33} was launched in 1994 and its still active GRB instrument is Konus.
Astro-Rivelatore Gamma a Immagini Leggero (AGILE) 11 /Super-AGILE \cite{grb34} was launched in
2007 and its Hard X-ray Imaging Detector (Super-AGILE) detected several GRBs.
CALorimetric Electron Telescope (CALET) 12 \cite{grb35} / Gamma-Ray Burst Monitor (CGBM), was launched in 2015 and it is placed on the International Space Station (ISS).

Monitor of All-sky X-ray Image (MAXI) 13 \cite{grb36}, started nominal observation in 2009. Its instrument Gas Slit Camera (GSC) detects GRBs. The instrument is placed on ISS.
Gamma-ray Burst Polarimeter POLAR 14 \cite{grb37}, was launched in 2016 and is dedicated to the measurement of GRB polarization.
Lomonosov 15 /BDRG \cite{grb38}, was launched in 2016. The BDRG instrument on board detected several GRBs.
The Hard X-ray Modulation Telescope (Insight-HXMT) 16 \cite{grb39}, was launched in 2017. It has on board the high energy X-ray telescope (HE), the medium energy X-ray telescope, and the low energy X-ray telescope.
ASTROSAT 17 \cite{grb40}, was launched in 2015 and its Cadmium Zinc Telluride Imager (CZTI) has already detected many GRBs.
Reuven Ramaty High Energy Solar Spectroscopic Imager (RHESSI) 18 \cite{grb41}, was launched in 2002. It is designed to study hard x-ray and gamma-ray emission from solar flares, however it is also efficient instrument to detect non-solar gamma-ray events like GRBs.
The energy range, FoV and localization accuracy for the instruments of the current missions which observe GRBs is summarized in Table 4. Figure 3 shows the FoV vs. localization accuracy of the current instruments which detect GRBs. For comparison the specification of this project is shown as
well.

@@

Our project can potentially contribute to some of the currently operating GRB collection and alertnetworks such as the following ones:
The InterPlanetary Network (IPN) 27 \cite{grb42} which derives the positions of fast gamma-ray transients of all kinds by triangulation. Numerous spacecraft and instruments participate in the network at the Earth’s orbit as well as in the interplanetary space. It detects about 350/year.
The Gamma-ray Coordinates Network (Transient Astronomy Network) (GCN/TAN) 28 provides information about GRBs in real-time to the world community. The network provides the real-time (and near real-time) distribution of GRB locations, images, spectra, and lightcurves detected by various spacecraft and the distribution of follow-up observation reports.
The Global Relay of Observatories Watching Transients Happen (GROWTH) 29 is an international scientific collaborative project studying the astronomical transients.

@@

This cubesat project will provide high precision localization accuracy of GRBs allowing efficient follow-up observations by existing ground based observatories. There are several observatories world-wide to perform photometric or spectroscopic observations of GRB afterglows, for example:
The Mobile Astronomical System of TElescope Robots (MASTER) 30 \cite{grb43} is a global network of robotic telescopes for very fast positioning and follow up of GRBs.
The Burst Optical Observer and Transient Exploring System (BOOTES) network of robotic telescopes for follow up observations of GRBs. 31 \cite{grb44} is a world wide The Robotic Optical Transient Search Experiment (ROTSE) 32 [101] are telescopes which operate at
sites around the world and follow GRBs.
Pi of the Sky 33 [102] is a system of detectors designed for continuous observation of night sky looking for optical flashes of astrophysical origin, in particular for GRBs.
Several other telescopes and observatories which provide measurements in optical, infra-red or radio bands are also, e.g.: Gamma-Ray Burst Optical/Near-Infrared Detector (GROND) 34 , the Palomar 60 inch telescope 35 , Rapid Eye Mount (REM) 36 , Livermore Optical Transient Imaging System (Super- LOTIS) 37 , Télescopes à Action Rapide pour les Objets Transitoires (TAROT) 38 , Gran Telescopio Canarias (GTC) 39 , ESO Very Large Telescope (VLT) 40 , Nordic Optical Telescope (NOT) 41 , Observatorio Astronómico Nacional on the Sierra de San Pedro Mártir 42 , Cerro Tololo Inter-American Observatory (CTIO) 43 , Telescopio Nazionale Galileo (TNG) 44 , Gao-Mei-Gu (GMG) station of Yunnan Observatories 45 , Observatorio de Sierra Nevada (OSN) 46 , United Kingdom Infrared Telescope (UKIRT) 47 , Very Large Array (VLA) 48 , Atacama Large Millimeter/Submillimeter Array (ALMA) 49 , James Clerk Maxwell Telescope 50 , Arcminute Microkelvin Imager which robotically triggers on Swift GRBs (AMI-GRB) 51 .

\subsection{The CAMELOT satellite}

There would most likely be four scintillators on the CAMELOT satellite. On two neighbouring sides of the satellite have two scintillators each. The scintillator will have a case either from aluminium or carbon fibre.

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/satellite_modules.png}
\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
\end{figure}

\begin{itemize}
\item The CubeSat platform has the following Sub-systems level elements, Figure 5 shows the sub-systems
of the CubeSat platform.
\item On-Board Computer [OBC] is responsible for control all the satellite’s sub-systems. OBC collects housekeeping and payload data and archives them in its internal storage.
\item Electrical Power System [EPS] is responsible for managing primary and secondary power sources and distributing power at appropriate voltage levels to on-board subsystems.
\item COM UHF Transceiver [COM] provides an RF communication link between the Ground Segment and the satellite. The COM codes the received messages from the OBC and transmits to the Ground Segment. Furthermore, the COM decodes the received RF messages from the Ground Segment and transmits to the OBC.
\item Attitude Determination and Control System [ADCS] determines and controls the satellite attitude.
\item Auxiliary Electronics [AUX] subsystems control the deploying mechanisms and monitor the
solar arrays. The Aux subsystem also contains the rigid backplane of the satellite; therefore, it also connects the subsystems.
\item Structure [STRU]
\item Ground Support Equipment [EGSE]
\end{itemize}

\subsection{The detection of GRBs}

The current detector design is a combination of CsI scintillators reaodout by the Multi Pixel Photon Counter (MPPC), which is a kind of the Silicon Photomultiplier device. The advantage of this system is a high light output with compact readout area. For the localization of GRB, photon statistics is one of important issue. Therefore, we need as much light yield as possible. Also, since the detector mounting area for the 3U cubesat standard is limited to be $\sim$300x75x5 mm$^{3}$ as described in the beginning of this section, a compact readout device is required. Currently, we are evaluating the detector performance using a sample of detector system consist of CsI(Tl) scintillator with a dimension of 150x75x5 mm$^{2}$ readout by Hamamatsu MPPC (latest model: S13360-6050CS with an effective area of 6x6 mm$^{2}$). \ref{fig:schem} shows a schematic picture of the location of one side of the detector and actual setup of performance evaluation test.

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/scint_on_sate.png}
\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
\end{figure}

It is challenging to readout the scintillation photons for such geometrically large and thin crystal with small readout area because the produced scintillation photons would be suffered by the multiple scattering inside the crystal before reaching the readout area of the MPPC. This would degrade the final light yield and affect to the performance of the energy resolution and lower energy threshold. In order to overcome this problem, we are planning to apply a multi-channel coincidence readout technique. A multi-channel readout increases the readout area and final light yield, simply and improvement of the uniformity of the light yield with respect to the incident gamma-ray position would be expected. However, increasing of the readout channel also increase the leakage current, which would be proportional to the readout area. The coincidence readout technique would be expected to suppress the effect of the increasing of the leakage current in the resultant spectrum.

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/histo_for_det.png}
\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
\end{figure}

Figure 23 shows the latest result of the study of this technique by irradiating 241Am radioisotope. Black and red data show the result by the single channel and 2-channel coincidence readout the single channel readout, respectively. As one can see obviously, the final light yield corresponding to the 59.5 keV gamma-ray photo absorption peak increases by almost 50 \% for the 2-channel readout. By scaling  the 2-channel readout result to the single channel readout for the 59.5 keV peak as shown by the blue curve, we found that the energy resolution improved thanks to the improvement of the uniformity of the position dependence of the light yield. Finally, we confirmed that the lower energy threshold for both readout technique achieved to be about 10 keV. Further improvement of the uniformity and/or lower energy threshold could be possible by optimizing the install location of the MPPC device.

@@

\subsection{The Geant4 platform}

Geant4 \cite{geant1, geant2, geant3} (for GEometry ANd Tracking) is a platform for "the simulation of the passage of particles through matter," using Monte Carlo methods. It is the successor of the GEANT series of software toolkits developed by CERN, and the first to use object oriented programming (in C++). Its development, maintenance and user support are taken care by the international Geant4 Collaboration. Application areas include high energy physics and nuclear experiments, medical, accelerator and space physics studies. The software is used by a number of research projects around the world.

The Geant4 software and source code is freely available from the project web site; until version 8.1 (released June 30, 2006), no specific software license for its use existed; Geant4 is now provided under the Geant4 Software License.

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/AtlasHalf.jpg}
\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
\end{figure}

Geant4 includes facilities for handling geometry, tracking, detector response, run management, visualization and user interface. For many physics simulations, this means less time needs to be spent on the low level details, and researchers can start immediately on the more important aspects of the simulation.

Following is a summary of each of the facilities listed above:

Geometry is an analysis of the physical layout of the experiment, including detectors, absorbers, etc., and considering how this layout will affect the path of particles in the experiment.
Tracking is simulating the passage of a particle through matter. This involves considering possible interactions and decay processes.
Detector response is recording when a particle passes through the volume of a detector, and approximating how a real detector would respond.
Run management is recording the details of each run (a set of events), as well as setting up the experiment in different configurations between runs.
Geant4 offers a number of options for visualization, including OpenGL, and a familiar user interface, based on Tcsh.
Geant4 can also perform basic histogramming; it requires external analysis tools or software that implements the AIDA framework for exploiting advanced histogramming features.

Since release 10.0, Geant4 implements multithreading, making use of thread-local storage to allow for efficient generation of simulated events in parallel.

Because of its general purpose nature, Geant4 is well suited for development of computational tools for analysing interactions of particle with matter in many areas. These include:

Space applications where it is used to study interactions between the natural space radiation environment and space hardware or astronauts;
Medical applications where interactions of radiations used for treatment are simulated.
Radiation effects in microelectronics where ionizing effects on semiconductor devices are modeled.
Nuclear physics

@@

\begin{figure}
\centering
\includegraphics[width=140.0mm]{images/fluovsnofluo.png}
\caption{The positions of irradiation for the investigation of the response of the scintillator}
\end{figure}

@@

\begin{figure}[htbp]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=0.45\textwidth,origin=c,angle=0]{images/alt_600km_AE-8_MIN_averaged_spectra.png}
 \qquad
 \includegraphics[width=.45\textwidth,origin=c]{images/alt_600km_AE-8_MAX_averaged_spectra.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:i} The scintillator on the left and the box holding the setup on the right}
 \end{figure}

@@

\begin{figure}[htbp]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=.45\textwidth,origin=c,angle=0]{images/alt_600km_AP-8_MIN_averaged_spectra.png}
 \qquad
 \includegraphics[width=.45\textwidth,origin=c]{images/alt_600km_AP-8_MAX_averaged_spectra.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:i} The scintillator on the left and the box holding the setup on the right}
 \end{figure}

@@

Gabor Galg\'oczi would like to thank Bal\'azs \'Ujv\'ari for the fruitful discussions they had on Geant4 simulations. András Pál made vital comments on the description of the electronics. Last but not least the author would like to thank Norbert Werner for the continued contributions to this work.

@@

\bibitem{grb1} Mészáros P., 2006, Reports on Progress in Physics, 69, 2259
%https://link.springer.com/content/pdf/10.1007/s11214-017-0366-4.pdf

\bibitem{grb2} Vedrenne G., \& Atteia J.-L., 2009, Gamma-Ray Bursts: The brightest explosions in the Universe,
Springer Praxis Books in Astronomy and Planetary Sciences, Published in association with Praxis
Publishing, UK
%https://link.springer.com/content/pdf/10.1007/s11214-017-0366-4.pdf

\bibitem{grb3} Kouveliotou C., Wijers R. A. M. J., \& Woosley S., 2012, Gamma-ray Bursts, Cambridge, UK:
Cambridge University Press
%https://link.springer.com/content/pdf/10.1007/s11214-017-0366-4.pdf

\bibitem{grb4} Gehrels N., \& Mészáros P. 2012, Science, 337, 932
%https://link.springer.com/content/pdf/10.1007/s11214-017-0366-4.pdf

\bibitem{grb5} Klebesadel R. W., Strong I. B., \& Olson R. A. 1973, The Astrophysical Journal, 182, L85

\bibitem{grb6} Kouveliotou C., Meegan C. A., Fishman G. J., et al. 1993, The Astrophysical Journal Letters, 413, L101

\bibitem{grb7} Balázs L. G., Bagoly Z., Horváth I., et al. 2003, Astronomy and Astrophysics, 401, 129

\bibitem{grb8} Mészáros A., Bagoly Z., Balázs L. G., \& Horváth I. 2006, Astronomy and Astrophysics, 455, 785

\bibitem{grb9} Berger E. 2014, Annual Review of Astronomy and Astrophysics, 52, 43

\bibitem{grb10} Rees M. J., \& Meszaros P. 1994, The Astrophysical Journal, 430, L93

\bibitem{grb11} van Paradijs J., Groot P. J., Galama T., et al. 1997, Nature, 386, 686

\bibitem{grb12} Paczynski B. 1986, The Astrophysical Journal, 308, L43

\bibitem{grb13} Woosley S. E., \& Bloom J. S. 2006, Annual Review of Astronomy \& Astrophysics, 44, 507

\bibitem{grb14} Fruchter A. S., Levan A. J., Strolger L., et al. 2006, Nature, 441, 463

\bibitem{grb15} Harrison F. A., Bloom J. S., Frail D. A. et al. 1999, The Astrophysical Journal Letters, 523, L121

\bibitem{grb16} Burrows D. N., Grupe D., Capalbi M., et al. 2006, The Astrophysical Journal, 653, 468

\bibitem{grb17} Abbott B. P., Abbott R., Abbott T. D., et al. 2017, Physical Review Letters, 119, 161101

\bibitem{grb18} Tanvir N. R., Levan A. J., Fruchter A. S., et al. 2013, Nature, 500, 547

\bibitem{grb19} Zhang, B. 2011, Comptes Rendus Physique, 12, 206

\bibitem{grb20} Toma, K., Yoon, S.-C., \& Bromm, V. 2016, Space Science Reviews, 202, 159

\bibitem{grb21} Goldstein A., et al., 2017, The Astrophysical Journal Letters, 848, L14

\bibitem{grb22} Savchenko V., et al., 2017, The Astrophysical Journal Letters, 848, L15

\bibitem{grb23} Troja E., et al., 2017, Naure, 551, 71

\bibitem{grb24} Evans P. A., Cenko S. B., Kennea J. A., et al. 2017, Science, 358, 1565

\bibitem{grb25} Loeb A., 2016, The Astrophysical Journal Letters, 819, L21

\bibitem{grb26} KAGRA Collaboration, Akutsu T., Ando M., et al. 2017, arXiv:1710.04823

\bibitem{grb27} Cavallari E., \& Frontera F. 2017, Space Science Reviews, 212, 429

\bibitem{grb28} Atwood, W. B., \& GLAST Collaboration 1994, Nuclear Instruments and Methods in Physics Research
A, 342, 302

\bibitem{grb30} Cavallari E., \& Frontera F. 2017, Space Science Reviews, 212, 429

\bibitem{grb31} Barthelmy S. D., Barbier L. M., Cummings J. R., et al. 2005, Space Science Reviews, 120, 143
